---
title: "README"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
```

## Packages used

```{r}
pkgs <- attachment::att_from_rscripts(path = ".", recursive = TRUE)
pkgs
```

Versions:

```{r}
installed.packages() %>%
  tibble::as_tibble() %>%
  dplyr::filter(Package %in% pkgs) %>%
  dplyr::select(Package, Version) %>%
  DT::datatable()
```

## Data used

Data for the dashboard came from a dataset provided during the DSSG 2019 hackathon. Data definition can be found here - https://docs.google.com/document/d/1-Db9evxYxdpHEG5P4h8UM3P8EC1W6PhMsFV3DBlHQOc/edit .

`stopwords-iso.json` are stopwords words for multiple languages I've found somewhere on GitHub lying around.


## Starting the app

This folder contains only the shiny part of the app. App itself depends on multiple cached files since otherwise computations are too intensive for app to be responsive.

In order to make app work, input dataset should be placed to folder `fbtrx_simple_csv` and named `fbtrx_simple.csv` (or you can provide your custom location at line 18 of `eda.R`). The format of the data should be identical to data definition above. Sourcing `eda.R` will create cached datasets and put them into `shiny` folder. Once it's done, you can start `app.R` with, e.g., RStudio "Run app" button or with `shiny::runApp('path/to/folder/shiny')`.
